Synthesizing Symmetric Lenses

### 2019-02-12 papers/BXProposal/main.tex

\begin{abstract}
Recent work has shown how to synthesize a class of string bijections from
regular expression specifications. These bijective string transformations
can be useful for synchronizing simple data formats, but many interesting
formats require non-bijective lenses. In this talk, we show how to expand
the class of synthesized transformations beyond bijections to a large subset
of full symmetric lenses (including all the standard asymmetric lenses)
using lightweight user annotations that help identify a ``bijective core.''
\end{abstract}

>>>>

\begin{abstract}
emph{AFM: I will remove this from the submission, but am including it in the
    document for people to review. It is due today (February 12)}
Recent work has shown how to synthesize a class of string bijections from
regular expression specifications. These bijective string transformations
can be useful for synchronizing simple data formats, but many interesting
formats require non-bijective lenses. In this talk, we show how to expand
the class of synthesized transformations beyond bijections to a large subset
of full symmetric lenses (including all the standard asymmetric lenses)
using lightweight user annotations that help identify a ``bijective core.''
\end{abstract}

### 2019-02-12 papers/SymmetricLenses/main.tex

\paragraph*{Relevance Annotations}\bcp{Wonder whether this should be its own
top-level section...?}\afm{I'm not sure, any other thoughts? To me it is
inherently an optimization, though it's a more important and interesting one
than others}
In this work, there are three competing constraints. The tool should (1) return
lenses quickly to users, (2) return the highest quality lenses, and (3)
not require users to write a large number of examples.
Our termination heuristic works well for most situations, but
there are cases where it fails.

>>>>

\paragraph*{Relevance Annotations}\bcp{Wonder whether this should be its own
top-level section...?}\afm{I'm not sure, any other thoughts? To me it is
inherently an optimization, though it's a more important and interesting one
than others}\bcp{My impression was that, before we invented these
annotations, things were really not working very well.  So they may be
``just an optimization,'' but they are a super-important one.  Moreover,
they strongly impact the way the user interacts with the system.  I think
they should figure prominently in the way we explain what we've done.}
In this work, there are three competing constraints. The tool should (1) return
lenses quickly to users, (2) return the highest quality lenses, and (3)
not require users to write a large number of examples.
Our termination heuristic works well for most situations, but
there are cases where it fails.
